Solent region: Test Maps

### 2021-08-05 Solent_Mapping_v2.Rmd
Changing chunk names so there are no duplicates

```{r Mapping the difference in fuel poverty from 2012 to 2018}
##BROKEN
merged_dfla$LA11CD <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
ggplot2::ggplot(la_Fuelpov20182012dif) +
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
labs(caption="Solent (all LA)")
```

@@

##### Looking at cities in more detail
```{r Southampton}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")

# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")

# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")

@@

#####Cities in More detail
```{r Southampton}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")

# plotting the gas consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Portsmouth")

# plotting the gas consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Winchester")

@@

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
head(lsoa_multidep)
lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf) +
  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
  scale_fill_continuous(name="IMD Score", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
#####Looking at the cities in more detail
```{r Looking at Southampton in more detail}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")

# plotting the multiple scales on dep of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `IMDScore`)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Looking at Portsmouth in more detail}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `IMDScore`)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Looking at Winchester in more detail}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Winchester")

# plotting the fuel poverty 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `IMDScore`)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference from 2010 to 2019

### Mapping Fuel Poverty
#### 2019
```{r Loading in the LSOA 2021 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2019<-readr::read_csv (inFile)
head(lsoa_fuelpov_2019)
```

```{r Mapping the LSOA 2019 Fuel Poverty}
lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
#####Looking at the cities in more detail
```{r Looking at Southampton in more detail}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Southampton")

# plotting the fuel poverty 2019 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Looking at Portsmouth in more detail}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Looking at Winchester in more detail}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Winchester")

@@

```{r Mapping the LSOA 2018 Fuel Poverty}
lsoa_fuelpov_2018$LSOA11CD <- lsoa_fuelpov_2018$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2018_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2018) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2018_merged$pcFP18 <- as.numeric(lsoa_fuelpov_2018_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2018_merged) +
  geom_sf(aes(fill=pcFP18))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs) 2018")
```
#####Looking at the cities in more detail
```{r Looking at Southampton in more detail}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Southampton")

# plotting the fuel poverty 2019 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Southampton 2018")
```
```{r Looking at Portsmouth in more detail}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth 2018")
```
```{r Looking at Winchester in more detail}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")

# plotting the fuel poverty 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester 2018")
```
####Mapping the difference in proportion of fuel poverty from 2012 to 2018
```{r Creating the dfference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2018
#Had to use 2018 as the metric for fuel poverty has changed in 2019 
#Red indicates an increase in fuel poverty from 2012 to 2018
fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
names(merged_df)
merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
summary(merged_df)
```
```{r Mapping the change in Fuel Poverty}
merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
ggplot2::ggplot(lsoa_fuelpov20122018) +
  geom_sf(aes(fill=pc_diff))+ 
  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
##### Looking at cities in more detail
```{r Looking at Southampton in more detail}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Southampton")
#Around Bargate and Freemantle increased fuel poverty
```
```{r Looking at Portsmouth in more detail}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
#Charles Dickens increased fuel poverty
```
```{r Looking at Winchester in more detail}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Winchester")

>>>>

```{r Mapping the difference in fuel poverty from 2012 to 2018}
##BROKEN
merged_dfla$lad18nm <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
ggplot2::ggplot(la_Fuelpov20182012dif) +
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
labs(caption="Solent (all LA)")
```

@@

##### Looking at cities in more detail
```{r Southampton LSOA Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Southampton")

# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Portsmouth")

# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean domestic electricity consumption \n(kWh per meter)`)) +
  scale_fill_continuous(name = "Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf, LAD11NM == "Winchester")

@@

#####Cities in More detail
```{r Southampton LSOA Gas}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Southampton")

# plotting the gas consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA Gas}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Portsmouth")

# plotting the gas consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Gas: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA Gas}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_merged_sf_gas, LAD11NM == "Winchester")

@@

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
head(lsoa_multidep)
lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf) +
  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
  scale_fill_continuous(name="IMD Score", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
#####Looking at the cities in more detail
```{r Southampton LSOA Indices of dep}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")

# plotting the multiple scales on dep of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `IMDScore`)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA Indices of dep}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Portsmouth")

# plotting the change in indices of dep from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `IMDScore`)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA Indices of dep}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Winchester")

# plotting the indices of dep 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `IMDScore`)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference from 2010 to 2019

### Mapping Fuel Poverty
#### 2019
```{r Loading in the LSOA 2019 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2019<-readr::read_csv (inFile)
head(lsoa_fuelpov_2019)
```

```{r Mapping the LSOA 2019 Fuel Poverty}
lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
#####Looking at the cities in more detail
```{r Southampton LSOA Fuel Pov 2019}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Southampton")

# plotting the fuel poverty 2019 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA Fuel Pov 2019}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA Fuel Pov}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Winchester")

@@

```{r Mapping the LSOA 2018 Fuel Poverty}
lsoa_fuelpov_2018$LSOA11CD <- lsoa_fuelpov_2018$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2018_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2018) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2018_merged$pcFP18 <- as.numeric(lsoa_fuelpov_2018_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2018_merged) +
  geom_sf(aes(fill=pcFP18))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs) 2018")
```
#####Looking at the cities in more detail
```{r Southampton LSOA Fuel Pov 2018}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Southampton")

# plotting the fuel poverty 2019 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Southampton 2018")
```
```{r Portsmouth LSOA Fuel Pov 2018}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth 2018")
```
```{r Winchester LOSA Fuel Pov 2018}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2018_merged, LAD11NM == "Winchester")

# plotting the fuel poverty 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pcFP18)) +
  scale_fill_continuous(name = "Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester 2018")
```
####Mapping the difference in proportion of fuel poverty from 2012 to 2018
```{r Creating the dfference in proportion variable}
#Green indicates a smaller increase in fuel poverty from 2012 to 2018
#Had to use 2018 as the metric for fuel poverty has changed in 2019 
#Red indicates an increase in fuel poverty from 2012 to 2018
fp_LSOA_2012_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2012 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2018_df <- readr::read_csv(paste0(dataFolder, "/Fuel Poverty/2018 LSOA_Fuel_Poverty.csv"))
fp_LSOA_2012_df$pc2012 <- fp_LSOA_2012_df$`Proportion of households fuel poor (%)`
fp_LSOA_2018_df$pc2018 <- fp_LSOA_2018_df$`Proportion of households fuel poor (%)`
merged_df <- merge(fp_LSOA_2012_df, fp_LSOA_2018_df, by = "LSOA Code", all = TRUE)
names(merged_df)
merged_df$pc_diff <-  as.numeric(merged_df$pc2018) - merged_df$pc2012
summary(merged_df)
```
```{r Mapping the change in Fuel Poverty}
merged_df$LSOA11CD <- merged_df$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov20122018 <- merge(lsoa_sf_data, merged_df) #merging these
ggplot2::ggplot(lsoa_fuelpov20122018) +
  geom_sf(aes(fill=pc_diff))+ 
  scale_fill_continuous(name="Change in Proportions of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
##### Looking at cities in more detail
```{r Southampton LSOA Fuel Pov 2012 2018}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Southampton")

# plotting the change in fuel poverty from 2018-2012 of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Southampton")
#Around Bargate and Freemantle increased fuel poverty
```
```{r Portsmouth LSOA Fuel Pov 2012 2018}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Portsmouth")

# plotting the change in fuel poverty from 2018-2012 of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
#Charles Dickens increased fuel poverty
```
```{r Winchester LSOA Fuel Pov 2012 2018}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov20122018, LAD11NM == "Winchester")
